---
title: "Calculate QCAE"
author: "Violet Kozloff"
date: "July 7, 2020"
output: html_document
---

Prepare workspace
```{r}
# install.packages("tidyverse", "here")
require(tidyverse)
require(here)

rm(list = ls())
```


Read, clean, and calculate scores for Canada data

```{r}
canada_data <- read.csv(here("Consolidated Questionnaire - English - CA_June 3, 2020_15.27.csv"))
clean_canada_data <- tibble(canada_data %>% select(Q1, QID39_1:QID39_31, QID58_1:QID58_31))
clean_canada_data <- clean_canada_data %>% rename_all(funs(str_replace(., "QID39", "child_qcae"  )))
clean_canada_data <- clean_canada_data %>% rename_all(funs(str_replace(., "QID58", "parent_qcae"  )))
clean_canada_data <- clean_canada_data %>% rename (unique_id = Q1)
clean_canada_data$unique_id <- str_c("canada_", clean_canada_data$unique_id)
# Reverse code
clean_canada_data <- clean_canada_data %>% mutate(child_qcae_1=recode(child_qcae_1, 
                         `Strongly Agree`="1",
                         `Slightly Agree`="2",
                         `Slightly Disagree`="3",
                         `Strongly Disagree`="4"))
clean_canada_data <- clean_canada_data %>% mutate(child_qcae_2=recode(child_qcae_2, 
                                                                 `Strongly Agree`="1",
                                                                 `Slightly Agree`="2",
                                                                 `Slightly Disagree`="3",
                                                                 `Strongly Disagree`="4"))
clean_canada_data <- clean_canada_data %>% mutate(child_qcae_17=recode(child_qcae_17, 
                                                                 `Strongly Agree`="1",
                                                                 `Slightly Agree`="2",
                                                                 `Slightly Disagree`="3",
                                                                 `Strongly Disagree`="4"))
clean_canada_data <- clean_canada_data %>% mutate(child_qcae_29=recode(child_qcae_29, 
                                                                  `Strongly Agree`="1",
                                                                  `Slightly Agree`="2",
                                                                  `Slightly Disagree`="3",
                                                                  `Strongly Disagree`="4"))
clean_canada_data <- clean_canada_data %>% mutate(parent_qcae_1=recode(parent_qcae_1, 
                                                                 `Strongly Agree`="1",
                                                                 `Slightly Agree`="2",
                                                                 `Slightly Disagree`="3",
                                                                 `Strongly Disagree`="4"))
clean_canada_data <- clean_canada_data %>% mutate(parent_qcae_2=recode(parent_qcae_2, 
                                                                 `Strongly Agree`="1",
                                                                 `Slightly Agree`="2",
                                                                 `Slightly Disagree`="3",
                                                                 `Strongly Disagree`="4"))
clean_canada_data <- clean_canada_data %>% mutate(parent_qcae_17=recode(parent_qcae_17, 
                                                                  `Strongly Agree`="1",
                                                                  `Slightly Agree`="2",
                                                                  `Slightly Disagree`="3",
                                                                  `Strongly Disagree`="4"))
clean_canada_data <- clean_canada_data %>% mutate(parent_qcae_29=recode(parent_qcae_29, 
                                                                  `Strongly Agree`="1",
                                                                  `Slightly Agree`="2",
                                                                  `Slightly Disagree`="3",
                                                                  `Strongly Disagree`="4"))
# Code numeric values
clean_canada_data <- clean_canada_data %>% mutate_all(funs(str_replace(., "Strongly Disagree", "1")))
clean_canada_data <- clean_canada_data %>% mutate_all(funs(str_replace(., "Slightly Disagree", "2")))
clean_canada_data <- clean_canada_data %>% mutate_all(funs(str_replace(., "Slightly Agree", "3")))
clean_canada_data <- clean_canada_data %>% mutate_all(funs(str_replace(., "Strongly Agree", "4")))
clean_canada_data <- clean_canada_data %>% slice(3:n())

# Calculate QCAE scores
clean_canada_data <- clean_canada_data %>% mutate(child_qcae_pt = as.numeric(child_qcae_15) + as.numeric(child_qcae_16)+as.numeric(child_qcae_19)+as.numeric(child_qcae_20) + as.numeric(child_qcae_21)+ as.numeric(child_qcae_22) + as.numeric(child_qcae_24) + as.numeric(child_qcae_25) + as.numeric(child_qcae_26) + as.numeric(child_qcae_27)) 
                                                  
clean_canada_data <- clean_canada_data %>% mutate(child_qcae_os = as.numeric(child_qcae_1) +
                                                    as.numeric(child_qcae_3) +as.numeric(child_qcae_4) +as.numeric(child_qcae_5) +
                                                    as.numeric(child_qcae_6) +as.numeric(child_qcae_18) +as.numeric(child_qcae_28) +as.numeric(child_qcae_30) +
                                                    as.numeric(child_qcae_31))
clean_canada_data <- clean_canada_data %>% mutate(child_qcae_cog = child_qcae_os + child_qcae_pt)

clean_canada_data <- clean_canada_data %>% mutate(child_qcae_ec = as.numeric(child_qcae_8) + as.numeric(child_qcae_9) +as.numeric(child_qcae_13) +
                                                    as.numeric(child_qcae_14))
clean_canada_data <- clean_canada_data %>% mutate(child_qcae_prox_r = as.numeric(child_qcae_7) + as.numeric(child_qcae_10) +as.numeric(child_qcae_12) +
                                                    as.numeric(child_qcae_23))
clean_canada_data <- clean_canada_data %>% mutate(child_qcae_periph_r = as.numeric(child_qcae_2) + as.numeric(child_qcae_11) +as.numeric(child_qcae_17) +
                                                    as.numeric(child_qcae_29))
clean_canada_data <- clean_canada_data %>% mutate(child_qcae_aff = child_qcae_ec + child_qcae_prox_r + child_qcae_periph_r)
clean_canada_data <- clean_canada_data %>% mutate(child_qcae_tot = child_qcae_aff+child_qcae_cog)
clean_canada_data <- clean_canada_data %>% mutate(parent_qcae_pt = as.numeric(parent_qcae_15) + as.numeric(parent_qcae_16) +as.numeric(parent_qcae_19) +
                                                    as.numeric(parent_qcae_20) +as.numeric(parent_qcae_21) +as.numeric(parent_qcae_22) +as.numeric(parent_qcae_24) +
                                                    as.numeric(parent_qcae_25) + as.numeric(parent_qcae_26) +as.numeric(parent_qcae_27))
clean_canada_data <- clean_canada_data %>% mutate(parent_qcae_os = as.numeric(parent_qcae_1) +
                                                    as.numeric(parent_qcae_3) +as.numeric(parent_qcae_4) +as.numeric(parent_qcae_5) +
                                                    as.numeric(parent_qcae_6) +as.numeric(parent_qcae_18) +as.numeric(parent_qcae_28) +as.numeric(parent_qcae_30) +
                                                    as.numeric(parent_qcae_31))
clean_canada_data <- clean_canada_data %>% mutate(parent_qcae_cog = parent_qcae_os + parent_qcae_pt)
clean_canada_data <- clean_canada_data %>% mutate(parent_qcae_ec = as.numeric(parent_qcae_8) + as.numeric(parent_qcae_9) +as.numeric(parent_qcae_13) +
                                                    as.numeric(parent_qcae_14))
clean_canada_data <- clean_canada_data %>% mutate(parent_qcae_prox_r = as.numeric(parent_qcae_7) + as.numeric(parent_qcae_10) +as.numeric(parent_qcae_12) +
                                                    as.numeric(parent_qcae_23))
clean_canada_data <- clean_canada_data %>% mutate(parent_qcae_periph_r = as.numeric(parent_qcae_2) + as.numeric(parent_qcae_11) +as.numeric(parent_qcae_17) +
                                                    as.numeric(parent_qcae_29))
clean_canada_data <- clean_canada_data %>% mutate(parent_qcae_aff = parent_qcae_ec + parent_qcae_prox_r + parent_qcae_periph_r)
clean_canada_data <- clean_canada_data %>% mutate(parent_qcae_tot = parent_qcae_aff+parent_qcae_cog)

clean_canada_data <- clean_canada_data %>% select (unique_id, child_qcae_os, child_qcae_pt, child_qcae_cog, child_qcae_ec, child_qcae_prox_r, child_qcae_periph_r, child_qcae_aff, child_qcae_tot,
                                                   parent_qcae_os, parent_qcae_pt, parent_qcae_cog, parent_qcae_ec, parent_qcae_prox_r, parent_qcae_periph_r, parent_qcae_aff, parent_qcae_tot)
```

Read, clean, and calculate scores for China data

```{r}                                                 
china_child_data <- read.csv(here("Parent QCAE - China_June 3, 2020_15.11.csv"))
clean_china_child_data <- tibble(china_child_data %>% select(Q2, Q1_1:Q1_31))
clean_china_child_data <- clean_china_child_data %>% rename_all(funs(str_replace(., "Q1", "child_qcae"  )))
clean_china_child_data <- clean_china_child_data %>% rename (unique_id = Q2)
clean_china_child_data$unique_id <- str_c("china_", clean_china_child_data$unique_id)
clean_china_child_data <- clean_china_child_data %>% slice(3:n())
china_parent_data <- read.csv(here("QCAE- China_June 3, 2020_15.15.csv"))
clean_china_parent_data <- tibble(china_parent_data %>% select(Q2, Q1_1:Q1_31))
clean_china_parent_data <- clean_china_parent_data %>% rename_all(funs(str_replace(., "Q1", "parent_qcae"  )))
clean_china_parent_data <- clean_china_parent_data %>% rename (unique_id = Q2)
clean_china_parent_data$unique_id <- str_c("china_", clean_china_parent_data$unique_id)
clean_china_parent_data <- clean_china_parent_data %>% slice(3:n())
clean_china_data <- full_join(clean_china_parent_data, clean_china_child_data, by = "unique_id")

# Reverse score
clean_china_data <- clean_china_data %>% mutate(child_qcae_1=recode(child_qcae_1, 
                                                                      `Strongly Agree`="1",
                                                                      `Slightly Agree`="2",
                                                                      `Slightly Disagree`="3",
                                                                      `Strongly Disagree`="4"))
clean_china_data <- clean_china_data %>% mutate(child_qcae_2=recode(child_qcae_2, 
                                                                      `Strongly Agree`="1",
                                                                      `Slightly Agree`="2",
                                                                      `Slightly Disagree`="3",
                                                                      `Strongly Disagree`="4"))
clean_china_data <- clean_china_data %>% mutate(child_qcae_17=recode(child_qcae_17, 
                                                                       `Strongly Agree`="1",
                                                                       `Slightly Agree`="2",
                                                                       `Slightly Disagree`="3",
                                                                       `Strongly Disagree`="4"))
clean_china_data <- clean_china_data %>% mutate(child_qcae_29=recode(child_qcae_29, 
                                                                       `Strongly Agree`="1",
                                                                       `Slightly Agree`="2",
                                                                       `Slightly Disagree`="3",
                                                                       `Strongly Disagree`="4"))
clean_china_data <- clean_china_data %>% mutate(parent_qcae_1=recode(parent_qcae_1, 
                                                                       `Strongly Agree`="1",
                                                                       `Slightly Agree`="2",
                                                                       `Slightly Disagree`="3",
                                                                       `Strongly Disagree`="4"))
clean_china_data <- clean_china_data %>% mutate(parent_qcae_2=recode(parent_qcae_2, 
                                                                       `Strongly Agree`="1",
                                                                       `Slightly Agree`="2",
                                                                       `Slightly Disagree`="3",
                                                                       `Strongly Disagree`="4"))
clean_china_data <- clean_china_data %>% mutate(parent_qcae_17=recode(parent_qcae_17, 
                                                                        `Strongly Agree`="1",
                                                                        `Slightly Agree`="2",
                                                                        `Slightly Disagree`="3",
                                                                        `Strongly Disagree`="4"))
clean_china_data <- clean_china_data %>% mutate(parent_qcae_29=recode(parent_qcae_29, 
                                                                        `Strongly Agree`="1",
                                                                        `Slightly Agree`="2",
                                                                        `Slightly Disagree`="3",
                                                                        `Strongly Disagree`="4"))
# Code numeric values
clean_china_data <- clean_china_data %>% mutate_all(funs(str_replace(., "Strongly Disagree", "1")))
clean_china_data <- clean_china_data %>% mutate_all(funs(str_replace(., "Slightly Disagree", "2")))
clean_china_data <- clean_china_data %>% mutate_all(funs(str_replace(., "Slightly Agree", "3")))
clean_china_data <- clean_china_data %>% mutate_all(funs(str_replace(., "Strongly Agree", "4")))
# Calculate subscale scores
clean_china_data <- clean_china_data %>% mutate(child_qcae_pt = as.numeric(child_qcae_15) + as.numeric(child_qcae_16) +as.numeric(child_qcae_19) +
                                                    as.numeric(child_qcae_20) +as.numeric(child_qcae_21) +as.numeric(child_qcae_22) +as.numeric(child_qcae_24) +
                                                    as.numeric(child_qcae_25) + as.numeric(child_qcae_26) +as.numeric(child_qcae_27))
clean_china_data <- clean_china_data %>% mutate(child_qcae_os = as.numeric(child_qcae_1) +
                                                    as.numeric(child_qcae_3) +as.numeric(child_qcae_4) +as.numeric(child_qcae_5) +
                                                    as.numeric(child_qcae_6) +as.numeric(child_qcae_18) +as.numeric(child_qcae_28) +as.numeric(child_qcae_30) +
                                                    as.numeric(child_qcae_31))
clean_china_data <- clean_china_data %>% mutate(child_qcae_cog = child_qcae_os + child_qcae_pt)

clean_china_data <- clean_china_data %>% mutate(child_qcae_ec = as.numeric(child_qcae_8) + as.numeric(child_qcae_9) +as.numeric(child_qcae_13) +
                                                    as.numeric(child_qcae_14))
clean_china_data <- clean_china_data %>% mutate(child_qcae_prox_r = as.numeric(child_qcae_7) + as.numeric(child_qcae_10) +as.numeric(child_qcae_12) +
                                                    as.numeric(child_qcae_23))
clean_china_data <- clean_china_data %>% mutate(child_qcae_periph_r = as.numeric(child_qcae_2) + as.numeric(child_qcae_11) +as.numeric(child_qcae_17) +
                                                    as.numeric(child_qcae_29))
clean_china_data <- clean_china_data %>% mutate(child_qcae_aff = child_qcae_ec + child_qcae_prox_r + child_qcae_periph_r)
clean_china_data <- clean_china_data %>% mutate(child_qcae_tot = child_qcae_aff+child_qcae_cog)
clean_china_data <- clean_china_data %>% mutate(parent_qcae_pt = as.numeric(parent_qcae_15) + as.numeric(parent_qcae_16) +as.numeric(parent_qcae_19) +
                                                    as.numeric(parent_qcae_20) +as.numeric(parent_qcae_21) +as.numeric(parent_qcae_22) +as.numeric(parent_qcae_24) +
                                                    as.numeric(parent_qcae_25) + as.numeric(parent_qcae_26) +as.numeric(parent_qcae_27))
clean_china_data <- clean_china_data %>% mutate(parent_qcae_os = as.numeric(parent_qcae_1) +
                                                    as.numeric(parent_qcae_3) +as.numeric(parent_qcae_4) +as.numeric(parent_qcae_5) +
                                                    as.numeric(parent_qcae_6) +as.numeric(parent_qcae_18) +as.numeric(parent_qcae_28) +as.numeric(parent_qcae_30) +
                                                    as.numeric(parent_qcae_31))
clean_china_data <- clean_china_data %>% mutate(parent_qcae_cog = parent_qcae_os + parent_qcae_pt)
clean_china_data <- clean_china_data %>% mutate(parent_qcae_ec = as.numeric(parent_qcae_8) + as.numeric(parent_qcae_9) +as.numeric(parent_qcae_13) +
                                                    as.numeric(parent_qcae_14))
clean_china_data <- clean_china_data %>% mutate(parent_qcae_prox_r = as.numeric(parent_qcae_7) + as.numeric(parent_qcae_10) +as.numeric(parent_qcae_12) +
                                                    as.numeric(parent_qcae_23))
clean_china_data <- clean_china_data %>% mutate(parent_qcae_periph_r = as.numeric(parent_qcae_2) + as.numeric(parent_qcae_11) +as.numeric(parent_qcae_17) +
                                                    as.numeric(parent_qcae_29))
clean_china_data <- clean_china_data %>% mutate(parent_qcae_aff = parent_qcae_ec + parent_qcae_prox_r + parent_qcae_periph_r)
clean_china_data <- clean_china_data %>% mutate(parent_qcae_tot = parent_qcae_aff+parent_qcae_cog)

clean_china_data <- clean_china_data %>% select (unique_id, child_qcae_os, child_qcae_pt, child_qcae_cog, child_qcae_ec, child_qcae_prox_r, child_qcae_periph_r, child_qcae_aff, child_qcae_tot,
                                                   parent_qcae_os, parent_qcae_pt, parent_qcae_cog, parent_qcae_ec, parent_qcae_prox_r, parent_qcae_periph_r, parent_qcae_aff, parent_qcae_tot)
```

Read, clean, and calculate scores for colombia data

```{r}
colombia_data <- read.csv(here("Colombia - All Questionnaires_June 30, 2020_12.24.csv"))
clean_colombia_data <- tibble(colombia_data %>% select(Q2, Q1_1:Q1_31, Q1_1.2:Q1_31.1)) %>%
  mutate (unique_id = paste0("colombia_", Q2)) %>%
  dplyr::rename(child_qcae_1 = Q1_1, child_qcae_2 = Q1_2, child_qcae_3 = Q1_3, child_qcae_4 = Q1_4, child_qcae_5 =  Q1_5, child_qcae_6 = Q1_6, child_qcae_7 = Q1_7, child_qcae_8 = Q1_8, child_qcae_9 =  Q1_9, child_qcae_10 =  Q1_10, child_qcae_11 = Q1_11, child_qcae_12 = Q1_12, child_qcae_13 = Q1_13, child_qcae_14 = Q1_14, child_qcae_15 = Q1_15, child_qcae_16 = Q1_16, child_qcae_17 = Q1_17,child_qcae_18 = Q1_18, child_qcae_19 = Q1_19, child_qcae_20 =  Q1_20, child_qcae_21 = Q1_21, child_qcae_22 = Q1_22, child_qcae_23 = Q1_23, child_qcae_24 =  Q1_24,  child_qcae_25 = Q1_25,child_qcae_26 =  Q1_26, child_qcae_27 = Q1_27, child_qcae_28 =  Q1_28,child_qcae_29 =Q1_29, child_qcae_30 = Q1_30, child_qcae_31 = Q1_31)%>%
  dplyr::rename(parent_qcae_1 = Q1_1.2, parent_qcae_2 = Q1_2.2, parent_qcae_3 = Q1_3.2, parent_qcae_4 = Q1_4.2, parent_qcae_5 =  Q1_5.2, parent_qcae_6 = Q1_6.2, parent_qcae_7 = Q1_7.2, parent_qcae_8 = Q1_8.2, parent_qcae_9 =  Q1_9.2, parent_qcae_10 =  Q1_10.2, parent_qcae_11 = Q1_11.1, parent_qcae_12 = Q1_12.1, parent_qcae_13 = Q1_13.1, parent_qcae_14 = Q1_14.1, parent_qcae_15 = Q1_15.1, parent_qcae_16 = Q1_16.1, parent_qcae_17 = Q1_17.1, parent_qcae_18 = Q1_18.1, parent_qcae_19 = Q1_19.1, parent_qcae_20 =  Q1_20.1, parent_qcae_21 = Q1_21.1, parent_qcae_22 = Q1_22.1, parent_qcae_23 = Q1_23.1, parent_qcae_24 =  Q1_24.1,  parent_qcae_25 = Q1_25.1, parent_qcae_26 =  Q1_26.1, parent_qcae_27 = Q1_27.1, parent_qcae_28 =  Q1_28.1, parent_qcae_29 = Q1_29.1, parent_qcae_30 = Q1_30.1, parent_qcae_31 = Q1_31.1) %>%
  select(-Q2)

# Reverse Code
clean_colombia_data <- clean_colombia_data %>% mutate(child_qcae_1=recode(child_qcae_1, 
                         `Muy de Acuerdo`="1",
                         `Ligeramente de Acuerdo`="2",
                         `Ligeramente en Desacuerdo`="3",
                         `Muy en Desacuerdo`="4"))

clean_colombia_data <- clean_colombia_data %>% mutate(child_qcae_2=recode(child_qcae_2, 
                         `Muy de Acuerdo`="1",
                         `Ligeramente de Acuerdo`="2",
                         `Ligeramente en Desacuerdo`="3",
                         `Muy en Desacuerdo`="4"))

clean_colombia_data <- clean_colombia_data %>% mutate(child_qcae_17=recode(child_qcae_17, 
                         `Muy de Acuerdo`="1",
                         `Ligeramente de Acuerdo`="17",
                         `Ligeramente en Desacuerdo`="3",
                         `Muy en Desacuerdo`="4"))

clean_colombia_data <- clean_colombia_data %>% mutate(child_qcae_29=recode(child_qcae_29, 
                         `Muy de Acuerdo`="1",
                         `Ligeramente de Acuerdo`="2",
                         `Ligeramente en Desacuerdo`="3",
                         `Muy en Desacuerdo`="4"))

clean_colombia_data <- clean_colombia_data %>% mutate(parent_qcae_1=recode(parent_qcae_1, 
                         `Muy de Acuerdo`="1",
                         `Ligeramente de Acuerdo`="2",
                         `Ligeramente en Desacuerdo`="3",
                         `Muy en Desacuerdo`="4"))

clean_colombia_data <- clean_colombia_data %>% mutate(parent_qcae_2=recode(parent_qcae_2, 
                         `Muy de Acuerdo`="1",
                         `Ligeramente de Acuerdo`="2",
                         `Ligeramente en Desacuerdo`="3",
                         `Muy en Desacuerdo`="4"))

clean_colombia_data <- clean_colombia_data %>% mutate(parent_qcae_17=recode(parent_qcae_17, 
                         `Muy de Acuerdo`="1",
                         `Ligeramente de Acuerdo`="17",
                         `Ligeramente en Desacuerdo`="3",
                         `Muy en Desacuerdo`="4"))

clean_colombia_data <- clean_colombia_data %>% mutate(parent_qcae_29=recode(parent_qcae_29, 
                         `Muy de Acuerdo`="1",
                         `Ligeramente de Acuerdo`="2",
                         `Ligeramente en Desacuerdo`="3",
                         `Muy en Desacuerdo`="4"))
# Code numeric values
clean_colombia_data <- clean_colombia_data %>% mutate_all(funs(str_replace_all(., "Muy en Desacuerdo", "1")))
clean_colombia_data <- clean_colombia_data %>% mutate_all(funs(str_replace_all(., "Ligeramente en Desacuerdo", "2")))
clean_colombia_data <- clean_colombia_data %>% mutate_all(funs(str_replace_all(., "Ligeramente de Acuerdo", "3")))
clean_colombia_data <- clean_colombia_data %>% mutate_all(funs(str_replace_all(., "Muy de Acuerdo", "4")))
clean_colombia_data <- clean_colombia_data %>% slice(3:n())

# Calculate QCAE scores
clean_colombia_data <- clean_colombia_data %>% mutate(child_qcae_pt = as.numeric(child_qcae_15) + as.numeric(child_qcae_16)
                                                  +as.numeric(child_qcae_19) + as.numeric(child_qcae_20) +as.numeric(child_qcae_21) +as.numeric(child_qcae_22) +as.numeric(child_qcae_24) +
                                                    as.numeric(child_qcae_25) + as.numeric(child_qcae_26) +as.numeric(child_qcae_27))


clean_colombia_data <- clean_colombia_data %>% mutate(child_qcae_os = as.numeric(child_qcae_1) +
                                                    as.numeric(child_qcae_3) +as.numeric(child_qcae_4) +as.numeric(child_qcae_5) +
                                                    as.numeric(child_qcae_6) +as.numeric(child_qcae_18) +as.numeric(child_qcae_28) +as.numeric(child_qcae_30) +
                                                    as.numeric(child_qcae_31))
clean_colombia_data <- clean_colombia_data %>% mutate(child_qcae_cog = child_qcae_os + child_qcae_pt)

clean_colombia_data <- clean_colombia_data %>% mutate(child_qcae_ec = as.numeric(child_qcae_8) + as.numeric(child_qcae_9) +as.numeric(child_qcae_13) +
                                                    as.numeric(child_qcae_14))
clean_colombia_data <- clean_colombia_data %>% mutate(child_qcae_prox_r = as.numeric(child_qcae_7) + as.numeric(child_qcae_10) +as.numeric(child_qcae_12) +
                                                    as.numeric(child_qcae_23))

clean_colombia_data <- clean_colombia_data %>% mutate(child_qcae_periph_r = as.numeric(child_qcae_2) + as.numeric(child_qcae_11) +as.numeric(child_qcae_17) +
                                                    as.numeric(child_qcae_29))

clean_colombia_data <- clean_colombia_data %>% mutate(child_qcae_aff = child_qcae_ec + child_qcae_prox_r + child_qcae_periph_r)

clean_colombia_data <- clean_colombia_data %>% mutate(child_qcae_tot = child_qcae_aff+child_qcae_cog)

clean_colombia_data <- clean_colombia_data %>% mutate(parent_qcae_pt = as.numeric(parent_qcae_15) + as.numeric(parent_qcae_16) +as.numeric(parent_qcae_19) +
                                                    as.numeric(parent_qcae_20) +as.numeric(parent_qcae_21) +as.numeric(parent_qcae_22) +as.numeric(parent_qcae_24) +
                                                    as.numeric(parent_qcae_25) + as.numeric(parent_qcae_26) +as.numeric(parent_qcae_27))
clean_colombia_data <- clean_colombia_data %>% mutate(parent_qcae_os = as.numeric(parent_qcae_1) +
                                                    as.numeric(parent_qcae_3) +as.numeric(parent_qcae_4) +as.numeric(parent_qcae_5) +
                                                    as.numeric(parent_qcae_6) +as.numeric(parent_qcae_18) +as.numeric(parent_qcae_28) +as.numeric(parent_qcae_30) +
                                                    as.numeric(parent_qcae_31))
clean_colombia_data <- clean_colombia_data %>% mutate(parent_qcae_cog = parent_qcae_os + parent_qcae_pt)
clean_colombia_data <- clean_colombia_data %>% mutate(parent_qcae_ec = as.numeric(parent_qcae_8) + as.numeric(parent_qcae_9) +as.numeric(parent_qcae_13) +
                                                    as.numeric(parent_qcae_14))
clean_colombia_data <- clean_colombia_data %>% mutate(parent_qcae_prox_r = as.numeric(parent_qcae_7) + as.numeric(parent_qcae_10) +as.numeric(parent_qcae_12) +
                                                    as.numeric(parent_qcae_23))
clean_colombia_data <- clean_colombia_data %>% mutate(parent_qcae_periph_r = as.numeric(parent_qcae_2) + as.numeric(parent_qcae_11) +as.numeric(parent_qcae_17) +
                                                    as.numeric(parent_qcae_29))
clean_colombia_data <- clean_colombia_data %>% mutate(parent_qcae_aff = parent_qcae_ec + parent_qcae_prox_r + parent_qcae_periph_r)
clean_colombia_data <- clean_colombia_data %>% mutate(parent_qcae_tot = parent_qcae_aff+parent_qcae_cog)

clean_colombia_data <- clean_colombia_data %>% select (unique_id, child_qcae_os, child_qcae_pt, child_qcae_cog, child_qcae_ec, child_qcae_prox_r, child_qcae_periph_r, child_qcae_aff, child_qcae_tot,
                                                   parent_qcae_os, parent_qcae_pt, parent_qcae_cog, parent_qcae_ec, parent_qcae_prox_r, parent_qcae_periph_r, parent_qcae_aff, parent_qcae_tot)
```

Read, clean, and calculate scores for Jordan data

```{r}
jordan_data <- read.csv(here("jordan qualtrics.csv"))
clean_jordan_data <- jordan_data %>% rename_all(funs(str_replace(., "QCAEchild", "child_qcae"  )))
clean_jordan_data <- clean_jordan_data %>% rename_all(funs(str_replace(., "QCAEparent", "parent_qcae")))
clean_jordan_data <- clean_jordan_data %>% rename (unique_id = 誰..Subject)%>%
  select(unique_id, child_qcae_1:child_qcae_31, parent_qcae_1:parent_qcae_31)
clean_jordan_data$unique_id <- str_c("jordan_", clean_jordan_data$unique_id)

# Recode values
add.1 <- function(x, na.rm=FALSE) (x+1)
clean_jordan_data <- clean_jordan_data %>% mutate_if(is.integer, add.1, na.rm = TRUE)

# Reverse code
clean_jordan_data <- clean_jordan_data %>% mutate(child_qcae_1=abs(child_qcae_1-5))
clean_jordan_data <- clean_jordan_data %>% mutate(child_qcae_2=abs(child_qcae_2-5))
clean_jordan_data <- clean_jordan_data %>% mutate(child_qcae_17=abs(child_qcae_17-5))
clean_jordan_data <- clean_jordan_data %>% mutate(child_qcae_29=abs(child_qcae_29-5))
clean_jordan_data <- clean_jordan_data %>% mutate(parent_qcae_1=abs(parent_qcae_1-5))
clean_jordan_data <- clean_jordan_data %>% mutate(parent_qcae_2=abs(parent_qcae_2-5))
clean_jordan_data <- clean_jordan_data %>% mutate(parent_qcae_17=abs(parent_qcae_17-5))
clean_jordan_data <- clean_jordan_data %>% mutate(parent_qcae_29=abs(parent_qcae_29-5))

# Calculate subscale values
clean_jordan_data <- clean_jordan_data %>% mutate(child_qcae_pt = as.numeric(child_qcae_15) + as.numeric(child_qcae_16) +as.numeric(child_qcae_19) +
                                                    as.numeric(child_qcae_20) +as.numeric(child_qcae_21) +as.numeric(child_qcae_22) +as.numeric(child_qcae_24) +
                                                    as.numeric(child_qcae_25) + as.numeric(child_qcae_26) +as.numeric(child_qcae_27))

clean_jordan_data <- clean_jordan_data %>% mutate(child_qcae_os = as.numeric(child_qcae_1) +
                                                    as.numeric(child_qcae_3) +as.numeric(child_qcae_4) +as.numeric(child_qcae_5) +
                                                    as.numeric(child_qcae_6) +as.numeric(child_qcae_18) +as.numeric(child_qcae_28) +as.numeric(child_qcae_30) +
                                                    as.numeric(child_qcae_31))

clean_jordan_data <- clean_jordan_data %>% mutate(child_qcae_cog = child_qcae_os + child_qcae_pt)

clean_jordan_data <- clean_jordan_data %>% mutate(child_qcae_ec = as.numeric(child_qcae_8) + as.numeric(child_qcae_9) +as.numeric(child_qcae_13) +
                                                    as.numeric(child_qcae_14))
clean_jordan_data <- clean_jordan_data %>% mutate(child_qcae_prox_r = as.numeric(child_qcae_7) + as.numeric(child_qcae_10) +as.numeric(child_qcae_12) +
                                                    as.numeric(child_qcae_23))

clean_jordan_data <- clean_jordan_data %>% mutate(child_qcae_periph_r = as.numeric(child_qcae_2) + as.numeric(child_qcae_11) +as.numeric(child_qcae_17) +
                                                    as.numeric(child_qcae_29))

clean_jordan_data <- clean_jordan_data %>% mutate(child_qcae_aff = child_qcae_ec + child_qcae_prox_r + child_qcae_periph_r)
clean_jordan_data <- clean_jordan_data %>% mutate(child_qcae_tot = child_qcae_aff+child_qcae_cog)
clean_jordan_data <- clean_jordan_data %>% mutate(parent_qcae_pt = as.numeric(parent_qcae_15) + as.numeric(parent_qcae_16) +as.numeric(parent_qcae_19) +
                                                    as.numeric(parent_qcae_20) +as.numeric(parent_qcae_21) +as.numeric(parent_qcae_22) +as.numeric(parent_qcae_24) +
                                                    as.numeric(parent_qcae_25) + as.numeric(parent_qcae_26) +as.numeric(parent_qcae_27))
clean_jordan_data <- clean_jordan_data %>% mutate(parent_qcae_os = as.numeric(parent_qcae_1) +
                                                    as.numeric(parent_qcae_3) +as.numeric(parent_qcae_4) +as.numeric(parent_qcae_5) +
                                                    as.numeric(parent_qcae_6) +as.numeric(parent_qcae_18) +as.numeric(parent_qcae_28) +as.numeric(parent_qcae_30) +
                                                    as.numeric(parent_qcae_31))
clean_jordan_data <- clean_jordan_data %>% mutate(parent_qcae_cog = parent_qcae_os + parent_qcae_pt)
clean_jordan_data <- clean_jordan_data %>% mutate(parent_qcae_ec = as.numeric(parent_qcae_8) + as.numeric(parent_qcae_9) +as.numeric(parent_qcae_13) +
                                                    as.numeric(parent_qcae_14))
clean_jordan_data <- clean_jordan_data %>% mutate(parent_qcae_prox_r = as.numeric(parent_qcae_7) + as.numeric(parent_qcae_10) +as.numeric(parent_qcae_12) +
                                                    as.numeric(parent_qcae_23))
clean_jordan_data <- clean_jordan_data %>% mutate(parent_qcae_periph_r = as.numeric(parent_qcae_2) + as.numeric(parent_qcae_11) +as.numeric(parent_qcae_17) +
                                                    as.numeric(parent_qcae_29))
clean_jordan_data <- clean_jordan_data %>% mutate(parent_qcae_aff = parent_qcae_ec + parent_qcae_prox_r + parent_qcae_periph_r)
clean_jordan_data <- clean_jordan_data %>% mutate(parent_qcae_tot = parent_qcae_aff+parent_qcae_cog)

clean_jordan_data <- clean_jordan_data %>% select (unique_id, child_qcae_os, child_qcae_pt, child_qcae_cog, child_qcae_ec, child_qcae_prox_r, child_qcae_periph_r, child_qcae_aff, child_qcae_tot,
                                                   parent_qcae_os, parent_qcae_pt, parent_qcae_cog, parent_qcae_ec, parent_qcae_prox_r, parent_qcae_periph_r, parent_qcae_aff, parent_qcae_tot)
```

Read, clean, and calculate scores for South Africa data

```{r}
south_africa_data <- read.csv(here("South Africa - All Questionnaires_June 3, 2020_15.35.csv"))
clean_south_africa_data <- tibble(south_africa_data %>% select(Q30, Q1_1:Q1_31, Q1_1.2:Q1_31.1))
clean_south_africa_data <- clean_south_africa_data %>% rename_all(funs(str_replace(., "Q1_", "qcae_")))
clean_south_africa_data <- clean_south_africa_data %>% rename (unique_id = Q30)
clean_south_africa_data$unique_id <- str_c("south_africa_", clean_south_africa_data$unique_id)
# Reverse code
clean_south_africa_data <- clean_south_africa_data %>% mutate(qcae_1=recode(qcae_1, 
                                                          `Strongly Agree`="1",
                                                          `Slightly Agree`="2",
                                                          `Slightly Disagree`="3",
                                                          `Strongly Disagree`="4"))
clean_south_africa_data <- clean_south_africa_data %>% mutate(qcae_2=recode(qcae_2, 
                                                          `Strongly Agree`="1",
                                                          `Slightly Agree`="2",
                                                          `Slightly Disagree`="3",
                                                          `Strongly Disagree`="4"))
clean_south_africa_data <- clean_south_africa_data %>% mutate(qcae_17=recode(qcae_17, 
                                                           `Strongly Agree`="1",
                                                           `Slightly Agree`="2",
                                                           `Slightly Disagree`="3",
                                                           `Strongly Disagree`="4"))
clean_south_africa_data <- clean_south_africa_data %>% mutate(qcae_29=recode(qcae_29, 
                                                           `Strongly Agree`="1",
                                                           `Slightly Agree`="2",
                                                           `Slightly Disagree`="3",
                                                           `Strongly Disagree`="4"))
clean_south_africa_data <- clean_south_africa_data %>% mutate(qcae_1.2=recode(qcae_1.2, 
                                                            `Strongly Agree`="1",
                                                            `Slightly Agree`="2",
                                                            `Slightly Disagree`="3",
                                                            `Strongly Disagree`="4"))
clean_south_africa_data <- clean_south_africa_data %>% mutate(qcae_2.2=recode(qcae_2.2, 
                                                            `Strongly Agree`="1",
                                                            `Slightly Agree`="2",
                                                            `Slightly Disagree`="3",
                                                            `Strongly Disagree`="4"))
clean_south_africa_data <- clean_south_africa_data %>% mutate(qcae_17.1=recode(qcae_17.1, 
                                                             `Strongly Agree`="1",
                                                             `Slightly Agree`="2",
                                                             `Slightly Disagree`="3",
                                                             `Strongly Disagree`="4"))
clean_south_africa_data <- clean_south_africa_data %>% mutate(qcae_29.1=recode(qcae_29.1, 
                                                             `Strongly Agree`="1",
                                                             `Slightly Agree`="2",
                                                             `Slightly Disagree`="3",
                                                             `Strongly Disagree`="4"))
# Find numeric scores for each item
clean_south_africa_data <- clean_south_africa_data %>% mutate_all(funs(str_replace(., "Strongly Disagree", "1")))
clean_south_africa_data <- clean_south_africa_data %>% mutate_all(funs(str_replace(., "Slightly Disagree", "2")))
clean_south_africa_data <- clean_south_africa_data %>% mutate_all(funs(str_replace(., "Slightly Agree", "3")))
clean_south_africa_data <- clean_south_africa_data %>% mutate_all(funs(str_replace(., "Strongly Agree", "4")))
clean_south_africa_data <- clean_south_africa_data %>% slice(3:n())
# Calculate subscales 
clean_south_africa_data <- clean_south_africa_data %>% mutate(child_qcae_pt = as.numeric(qcae_15) + as.numeric(qcae_16) +as.numeric(qcae_19) +
                                              as.numeric(qcae_20) +as.numeric(qcae_21) +as.numeric(qcae_22) +as.numeric(qcae_24) +
                                              as.numeric(qcae_25) + as.numeric(qcae_26) +as.numeric(qcae_27))
clean_south_africa_data <- clean_south_africa_data %>% mutate(child_qcae_os = as.numeric(qcae_1) +
                                              as.numeric(qcae_3) +as.numeric(qcae_4) +as.numeric(qcae_5) +
                                              as.numeric(qcae_6) +as.numeric(qcae_18) +as.numeric(qcae_28) +as.numeric(qcae_30) +
                                              as.numeric(qcae_31))
clean_south_africa_data <- clean_south_africa_data %>% mutate(child_qcae_cog = child_qcae_os + child_qcae_pt)

clean_south_africa_data <- clean_south_africa_data %>% mutate(child_qcae_ec = as.numeric(qcae_8) + as.numeric(qcae_9) +as.numeric(qcae_13) +
                                              as.numeric(qcae_14))
clean_south_africa_data <- clean_south_africa_data %>% mutate(child_qcae_prox_r = as.numeric(qcae_7) + as.numeric(qcae_10) +as.numeric(qcae_12) +
                                              as.numeric(qcae_23))
clean_south_africa_data <- clean_south_africa_data %>% mutate(child_qcae_periph_r = as.numeric(qcae_2) + as.numeric(qcae_11) +as.numeric(qcae_17) +
                                              as.numeric(qcae_29))
clean_south_africa_data <- clean_south_africa_data %>% mutate(child_qcae_aff = child_qcae_ec + child_qcae_prox_r + child_qcae_periph_r)
clean_south_africa_data <- clean_south_africa_data %>% mutate(child_qcae_tot = child_qcae_aff+child_qcae_cog)
clean_south_africa_data <- clean_south_africa_data %>% mutate(parent_qcae_pt = as.numeric(qcae_15.1) + as.numeric(qcae_16.1) +as.numeric(qcae_19.1) +
                                              as.numeric(qcae_20.1) +as.numeric(qcae_21.1) +as.numeric(qcae_22.1) +as.numeric(qcae_24.1) +
                                              as.numeric(qcae_25.1) + as.numeric(qcae_26.1) +as.numeric(qcae_27.1))
clean_south_africa_data <- clean_south_africa_data %>% mutate(parent_qcae_os = as.numeric(qcae_1.2) +
                                              as.numeric(qcae_3.2) +as.numeric(qcae_4.2) +as.numeric(qcae_5.2) +
                                              as.numeric(qcae_6.2) +as.numeric(qcae_18.1) +as.numeric(qcae_28.1) +as.numeric(qcae_30.1) +
                                              as.numeric(qcae_31.1))
clean_south_africa_data <- clean_south_africa_data %>% mutate(parent_qcae_cog = parent_qcae_os + parent_qcae_pt)
clean_south_africa_data <- clean_south_africa_data %>% mutate(parent_qcae_ec = as.numeric(qcae_8.2) + as.numeric(qcae_9.2) +as.numeric(qcae_13.1) +
                                              as.numeric(qcae_14.1))
clean_south_africa_data <- clean_south_africa_data %>% mutate(parent_qcae_prox_r = as.numeric(qcae_7.2) + as.numeric(qcae_10.2) +as.numeric(qcae_12.1) +
                                              as.numeric(qcae_23.1))
clean_south_africa_data <- clean_south_africa_data %>% mutate(parent_qcae_periph_r = as.numeric(qcae_2.2) + as.numeric(qcae_11.1) +as.numeric(qcae_17.1) +
                                              as.numeric(qcae_29.1))
clean_south_africa_data <- clean_south_africa_data %>% mutate(parent_qcae_aff = parent_qcae_ec + parent_qcae_prox_r + parent_qcae_periph_r)
clean_south_africa_data <- clean_south_africa_data %>% mutate(parent_qcae_tot = parent_qcae_aff+parent_qcae_cog)

clean_south_africa_data <- clean_south_africa_data %>% select (unique_id, child_qcae_os, child_qcae_pt, child_qcae_ec, child_qcae_prox_r, child_qcae_periph_r, child_qcae_aff,child_qcae_cog,child_qcae_tot,
                                             parent_qcae_os, parent_qcae_pt, parent_qcae_ec, parent_qcae_prox_r, parent_qcae_periph_r, parent_qcae_aff,parent_qcae_cog,parent_qcae_tot)
```

Read, clean, and calculate scores for Turkey data
``` {r}
turkey_toddler_data <- read.csv(here("Turkish_3-5years_merged_data_for_chicago_v1.csv"))
turkey_toddler_data <- tibble(turkey_toddler_data %>% select(誰..id_no, c_emp_1:c_emp_31, m_emp_1:m_emp_31))
turkey_child_data <- read.csv(here("Turkish_6-12years_merged_data_for_chicago_v1.csv"))
turkey_child_data <- tibble(turkey_child_data %>% select(誰..id_no, c_emp_1:c_emp_31, m_emp_1:m_emp_31))
turkey_data <- rbind(turkey_toddler_data, turkey_child_data)
clean_turkey_data <- turkey_data %>% rename_all(funs(str_replace(., "c_emp", "child_qcae"  )))
clean_turkey_data <- clean_turkey_data %>% rename_all(funs(str_replace(., "m_emp", "parent_qcae"  )))
clean_turkey_data <- clean_turkey_data %>% rename (unique_id = 誰..id_no)
clean_turkey_data$unique_id <- str_c("turkey_", clean_turkey_data$unique_id)

# Reverse code (assuming that raw data was not reverse coded and that each number in the raw data aligned with a likert scale value)
clean_turkey_data <- clean_turkey_data %>% mutate(child_qcae_1=5-child_qcae_1)
clean_turkey_data <- clean_turkey_data %>% mutate(child_qcae_2=5-child_qcae_2)
clean_turkey_data <- clean_turkey_data %>% mutate(child_qcae_17=5-child_qcae_17)
clean_turkey_data <- clean_turkey_data %>% mutate(child_qcae_29=5-child_qcae_29)
clean_turkey_data <- clean_turkey_data %>% mutate(parent_qcae_1=5-parent_qcae_1)
clean_turkey_data <- clean_turkey_data %>% mutate(parent_qcae_2=5-parent_qcae_2)
clean_turkey_data <- clean_turkey_data %>% mutate(parent_qcae_17=5-parent_qcae_17)
clean_turkey_data <- clean_turkey_data %>% mutate(parent_qcae_29=5-parent_qcae_29)

# Calculate subscales
clean_turkey_data <- clean_turkey_data %>% mutate(child_qcae_pt = as.numeric(child_qcae_15) + as.numeric(child_qcae_16) +as.numeric(child_qcae_19) +
                                                    as.numeric(child_qcae_20) +as.numeric(child_qcae_21) +as.numeric(child_qcae_22) +as.numeric(child_qcae_24) +
                                                    as.numeric(child_qcae_25) + as.numeric(child_qcae_26) +as.numeric(child_qcae_27))
clean_turkey_data <- clean_turkey_data %>% mutate(child_qcae_os = as.numeric(child_qcae_1) +
                                                    as.numeric(child_qcae_3) +as.numeric(child_qcae_4) +as.numeric(child_qcae_5) +
                                                    as.numeric(child_qcae_6) +as.numeric(child_qcae_18) +as.numeric(child_qcae_28) +as.numeric(child_qcae_30) +
                                                    as.numeric(child_qcae_31))
clean_turkey_data <- clean_turkey_data %>% mutate(child_qcae_cog = child_qcae_os + child_qcae_pt)

clean_turkey_data <- clean_turkey_data %>% mutate(child_qcae_ec = as.numeric(child_qcae_8) + as.numeric(child_qcae_9) +as.numeric(child_qcae_13) +
                                                    as.numeric(child_qcae_14))
clean_turkey_data <- clean_turkey_data %>% mutate(child_qcae_prox_r = as.numeric(child_qcae_7) + as.numeric(child_qcae_10) +as.numeric(child_qcae_12) +
                                                    as.numeric(child_qcae_23))
clean_turkey_data <- clean_turkey_data %>% mutate(child_qcae_periph_r = as.numeric(child_qcae_2) + as.numeric(child_qcae_11) +as.numeric(child_qcae_17) +
                                                    as.numeric(child_qcae_29))
clean_turkey_data <- clean_turkey_data %>% mutate(child_qcae_aff = child_qcae_ec + child_qcae_prox_r + child_qcae_periph_r)
clean_turkey_data <- clean_turkey_data %>% mutate(child_qcae_tot = child_qcae_aff+child_qcae_cog)
clean_turkey_data <- clean_turkey_data %>% mutate(parent_qcae_pt = as.numeric(parent_qcae_15) + as.numeric(parent_qcae_16) +as.numeric(parent_qcae_19) +
                                                    as.numeric(parent_qcae_20) +as.numeric(parent_qcae_21) +as.numeric(parent_qcae_22) +as.numeric(parent_qcae_24) +
                                                    as.numeric(parent_qcae_25) + as.numeric(parent_qcae_26) +as.numeric(parent_qcae_27))
clean_turkey_data <- clean_turkey_data %>% mutate(parent_qcae_os = as.numeric(parent_qcae_1) +
                                                    as.numeric(parent_qcae_3) +as.numeric(parent_qcae_4) +as.numeric(parent_qcae_5) +
                                                    as.numeric(parent_qcae_6) +as.numeric(parent_qcae_18) +as.numeric(parent_qcae_28) +as.numeric(parent_qcae_30) +
                                                    as.numeric(parent_qcae_31))
clean_turkey_data <- clean_turkey_data %>% mutate(parent_qcae_cog = parent_qcae_os + parent_qcae_pt)
clean_turkey_data <- clean_turkey_data %>% mutate(parent_qcae_ec = as.numeric(parent_qcae_8) + as.numeric(parent_qcae_9) +as.numeric(parent_qcae_13) +
                                                    as.numeric(parent_qcae_14))
clean_turkey_data <- clean_turkey_data %>% mutate(parent_qcae_prox_r = as.numeric(parent_qcae_7) + as.numeric(parent_qcae_10) +as.numeric(parent_qcae_12) +
                                                    as.numeric(parent_qcae_23))
clean_turkey_data <- clean_turkey_data %>% mutate(parent_qcae_periph_r = as.numeric(parent_qcae_2) + as.numeric(parent_qcae_11) +as.numeric(parent_qcae_17) +
                                                    as.numeric(parent_qcae_29))
clean_turkey_data <- clean_turkey_data %>% mutate(parent_qcae_aff = parent_qcae_ec + parent_qcae_prox_r + parent_qcae_periph_r)
clean_turkey_data <- clean_turkey_data %>% mutate(parent_qcae_tot = parent_qcae_aff+parent_qcae_cog)

clean_turkey_data <- clean_turkey_data %>% select (unique_id, child_qcae_os, child_qcae_pt, child_qcae_cog, child_qcae_ec, child_qcae_prox_r, child_qcae_periph_r, child_qcae_aff, child_qcae_tot,
                                                   parent_qcae_os, parent_qcae_pt, parent_qcae_cog, parent_qcae_ec, parent_qcae_prox_r, parent_qcae_periph_r, parent_qcae_aff, parent_qcae_tot)
```

Read, clean, and calculate scores for USA data
```{r}
usa_data <- read.csv(here("USA- All Questionnaires_June 3, 2020_15.34.csv"))
clean_usa_data <- tibble(usa_data %>% select(RecipientFirstName, Q1_1:Q1_31, Q1_1.2:Q1_31.1))
clean_usa_data <- clean_usa_data %>% rename_all(funs(str_replace(., "Q1_", "qcae_")))
clean_usa_data <- clean_usa_data %>% rename (unique_id = RecipientFirstName)
clean_usa_data$unique_id <- str_c("usa_", clean_usa_data$unique_id)
# Reverse score
clean_usa_data <- clean_usa_data %>% mutate(qcae_1=recode(qcae_1, 
                                                                    `Strongly Agree`="1",
                                                                    `Slightly Agree`="2",
                                                                    `Slightly Disagree`="3",
                                                                    `Strongly Disagree`="4"))
clean_usa_data <- clean_usa_data %>% mutate(qcae_2=recode(qcae_2, 
                                                                    `Strongly Agree`="1",
                                                                    `Slightly Agree`="2",
                                                                    `Slightly Disagree`="3",
                                                                    `Strongly Disagree`="4"))
clean_usa_data <- clean_usa_data %>% mutate(qcae_17=recode(qcae_17, 
                                                                     `Strongly Agree`="1",
                                                                     `Slightly Agree`="2",
                                                                     `Slightly Disagree`="3",
                                                                     `Strongly Disagree`="4"))
clean_usa_data <- clean_usa_data %>% mutate(qcae_29=recode(qcae_29, 
                                                                     `Strongly Agree`="1",
                                                                     `Slightly Agree`="2",
                                                                     `Slightly Disagree`="3",
                                                                     `Strongly Disagree`="4"))
clean_usa_data <- clean_usa_data %>% mutate(qcae_1.2=recode(qcae_1.2, 
                                                                     `Strongly Agree`="1",
                                                                     `Slightly Agree`="2",
                                                                     `Slightly Disagree`="3",
                                                                     `Strongly Disagree`="4"))
clean_usa_data <- clean_usa_data %>% mutate(qcae_2.2=recode(qcae_2.2, 
                                                                     `Strongly Agree`="1",
                                                                     `Slightly Agree`="2",
                                                                     `Slightly Disagree`="3",
                                                                     `Strongly Disagree`="4"))
clean_usa_data <- clean_usa_data %>% mutate(qcae_17.1=recode(qcae_17.1, 
                                                                      `Strongly Agree`="1",
                                                                      `Slightly Agree`="2",
                                                                      `Slightly Disagree`="3",
                                                                      `Strongly Disagree`="4"))
clean_usa_data <- clean_usa_data %>% mutate(qcae_29.1=recode(qcae_29.1, 
                                                                      `Strongly Agree`="1",
                                                                      `Slightly Agree`="2",
                                                                      `Slightly Disagree`="3",
                                                                      `Strongly Disagree`="4"))
# Code numeric values
clean_usa_data <- clean_usa_data %>% mutate_all(funs(str_replace(., "Strongly Disagree", "1")))
clean_usa_data <- clean_usa_data %>% mutate_all(funs(str_replace(., "Slightly Disagree", "2")))
clean_usa_data <- clean_usa_data %>% mutate_all(funs(str_replace(., "Slightly Agree", "3")))
clean_usa_data <- clean_usa_data %>% mutate_all(funs(str_replace(., "Strongly Agree", "4")))
clean_usa_data <- clean_usa_data %>% slice(3:n())
# Calculate subscale scores
clean_usa_data <- clean_usa_data %>% mutate(child_qcae_pt = as.numeric(qcae_15) + as.numeric(qcae_16) +as.numeric(qcae_19) +
                                                  as.numeric(qcae_20) +as.numeric(qcae_21) +as.numeric(qcae_22) +as.numeric(qcae_24) +
                                                  as.numeric(qcae_25) + as.numeric(qcae_26) +as.numeric(qcae_27))
clean_usa_data <- clean_usa_data %>% mutate(child_qcae_os = as.numeric(qcae_1) +
                                                  as.numeric(qcae_3) +as.numeric(qcae_4) +as.numeric(qcae_5) +
                                                  as.numeric(qcae_6) +as.numeric(qcae_18) +as.numeric(qcae_28) +as.numeric(qcae_30) +
                                                  as.numeric(qcae_31))
clean_usa_data <- clean_usa_data %>% mutate(child_qcae_cog = child_qcae_os + child_qcae_pt)

clean_usa_data <- clean_usa_data %>% mutate(child_qcae_ec = as.numeric(qcae_8) + as.numeric(qcae_9) +as.numeric(qcae_13) +
                                                  as.numeric(qcae_14))
clean_usa_data <- clean_usa_data %>% mutate(child_qcae_prox_r = as.numeric(qcae_7) + as.numeric(qcae_10) +as.numeric(qcae_12) +
                                                  as.numeric(qcae_23))
clean_usa_data <- clean_usa_data %>% mutate(child_qcae_periph_r = as.numeric(qcae_2) + as.numeric(qcae_11) +as.numeric(qcae_17) +
                                                  as.numeric(qcae_29))
clean_usa_data <- clean_usa_data %>% mutate(child_qcae_aff = child_qcae_ec + child_qcae_prox_r + child_qcae_periph_r)
clean_usa_data <- clean_usa_data %>% mutate(child_qcae_tot = child_qcae_aff+child_qcae_cog)
clean_usa_data <- clean_usa_data %>% mutate(parent_qcae_pt = as.numeric(qcae_15.1) + as.numeric(qcae_16.1) +as.numeric(qcae_19.1) +
                                                  as.numeric(qcae_20.1) +as.numeric(qcae_21.1) +as.numeric(qcae_22.1) +as.numeric(qcae_24.1) +
                                                  as.numeric(qcae_25.1) + as.numeric(qcae_26.1) +as.numeric(qcae_27.1))
clean_usa_data <- clean_usa_data %>% mutate(parent_qcae_os = as.numeric(qcae_1.2) +
                                                  as.numeric(qcae_3.2) +as.numeric(qcae_4.2) +as.numeric(qcae_5.2) +
                                                  as.numeric(qcae_6.2) +as.numeric(qcae_18.1) +as.numeric(qcae_28.1) +as.numeric(qcae_30.1) +
                                                  as.numeric(qcae_31.1))
clean_usa_data <- clean_usa_data %>% mutate(parent_qcae_cog = parent_qcae_os + parent_qcae_pt)
clean_usa_data <- clean_usa_data %>% mutate(parent_qcae_ec = as.numeric(qcae_8.2) + as.numeric(qcae_9.2) +as.numeric(qcae_13.1) +
                                                  as.numeric(qcae_14.1))
clean_usa_data <- clean_usa_data %>% mutate(parent_qcae_prox_r = as.numeric(qcae_7.2) + as.numeric(qcae_10.2) +as.numeric(qcae_12.1) +
                                                  as.numeric(qcae_23.1))
clean_usa_data <- clean_usa_data %>% mutate(parent_qcae_periph_r = as.numeric(qcae_2.2) + as.numeric(qcae_11.1) +as.numeric(qcae_17.1) +
                                                  as.numeric(qcae_29.1))
clean_usa_data <- clean_usa_data %>% mutate(parent_qcae_aff = parent_qcae_ec + parent_qcae_prox_r + parent_qcae_periph_r)
clean_usa_data <- clean_usa_data %>% mutate(parent_qcae_tot = parent_qcae_aff+parent_qcae_cog)

clean_usa_data <- clean_usa_data %>% select (unique_id, child_qcae_os, child_qcae_pt, child_qcae_ec, child_qcae_prox_r, child_qcae_periph_r, child_qcae_aff, child_qcae_cog, child_qcae_tot,
                                             parent_qcae_os, parent_qcae_pt, parent_qcae_ec, parent_qcae_prox_r, parent_qcae_periph_r, parent_qcae_aff,parent_qcae_cog,parent_qcae_tot)
```

Join all data
```{r}
output_data <- full_join(clean_canada_data, clean_china_data)
output_data <- full_join(output_data, clean_colombia_data)
output_data <- full_join(output_data, clean_jordan_data)
output_data <- full_join(output_data, clean_south_africa_data)
output_data <- full_join(output_data, clean_turkey_data)
output_data <- full_join(output_data, clean_usa_data)
```

Clean and write joined data to csv
```{r}
# Remove entries with invalid IDs
output_data <- output_data %>% filter(unique_id != "canada_" & unique_id != "china_" & unique_id != "usa_")
# Rename columns
output_data <- output_data %>% rename("vk_child_qcae_aff" = child_qcae_aff, "vk_child_qcae_cog" = child_qcae_cog, "vk_child_qcae_os" = child_qcae_os,
                                      "vk_child_qcae_pt" = child_qcae_pt, "vk_child_qcae_ec" = child_qcae_ec, "vk_child_qcae_tot" = child_qcae_tot,
                                      "vk_parent_qcae_aff" = parent_qcae_aff, "vk_parent_qcae_cog" = parent_qcae_cog, "vk_parent_qcae_os" = parent_qcae_os,
                                      "vk_parent_qcae_pt" = parent_qcae_pt, "vk_parent_qcae_ec" = parent_qcae_ec, "vk_parent_qcae_tot" = parent_qcae_tot)

# Remove any duplicate rows
output_data <- distinct(output_data)

# Remove duplicate entry with missing values from QCAE data
output_data <- output_data %>% 
  filter(!(is.na(vk_child_qcae_os) & (unique_id == "china_3021" | unique_id == "colombia_327" | unique_id == "colombia_353")))%>%
  filter(!(is.na(vk_parent_qcae_os) & unique_id == "colombia_164"))

# Remove duplicate entries with conflicting values from QCAE data
output_data <- output_data %>% 
  filter(!(unique_id == "china_3030"| unique_id == "south_africa_2069" | unique_id == "south_africa_2108" | unique_id == "south_africa_2116" | unique_id == "south_africa_4885"| unique_id == "china_3021" | unique_id == "colombia_137")) 

# Clean participant ID names
output_data <- output_data %>% 
  mutate(unique_id = str_remove_all(unique_id, "[# ]"))

# Uncomment to see any remaining duplicate entries with slightly different values
# View(output_data %>% add_count(unique_id) %>% filter(n>1))

write.csv(output_data, here("templeton_qcae_calculations.csv"))

```
